Group 9 Presentation

### 2021-12-06 presentation.Rmd
Added Random Forest and relative tree plot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

library(ISLR)
library(leaps)
library(tidyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)
library(class)
library(fastDummies)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(repos='http://cran.rstudio.org')
have.packages <- installed.packages()
cran.packages <- c('devtools','plotrix','randomForest','tree')
to.install <- setdiff(cran.packages, have.packages[,1])
if(length(to.install)>0) install.packages(to.install)

library(devtools)
if(!('reprtree' %in% installed.packages())){
  install_github('araastat/reprtree')
}
for(p in c(cran.packages, 'reprtree')) eval(substitute(library(pkg), list(pkg=p)))
```

@@

library(ISLR)
library(leaps)
library(tidyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)
library(class)
library(fastDummies)
library(reprtree)

@@

```{r}
rf_fit <- randomForest(as.factor(HeartDisease) ~ ., data = train, mtry = sqrt(ncol(train) - 1), importance = TRUE, type= "classification")

true <- test$HeartDisease
rf <- predict(rf_fit,test,type="class")

predicted2 <- ifelse(rf>0.5,1,0)

confm2<-table(predicted=rf,True=true)
kable(confm2)

paste("the overall fraction of correct predictions in the test dataset is :",(confm2[1,1]+confm2[2,2])/sum(confm2))

rf_fit
```

## Representative Tree Paper

```{r}
reprtree:::plot.getTree(rf_fit)
```
